---
title: 'RMarkdown:  In Class Assignment'
author: "YOUR NAME HERE"
date: "Data 2401"
output: 
  html_document:
    toc: TRUE
    toc_depth: 3
---


```{r setup, include=FALSE}
# Everything in this chunk is R code. 
# You are not expected to understand or edit this yet. 
# We will talk about what this does in a later class, with a little preview in part 2.
knitr::opts_chunk$set(echo = TRUE) 
```


Reminders: 

- You do not need to memorize Markdown syntax.
- You are expected to look things up using:
   - RStudio’s Markdown Help
   - Online documentation or examples
- Click Knit as you go to check that your document still renders correctly.
- Commit at the end, but consider committing as you go as well. 



# Part 1: Markdown Practice

**Do not skip reading this instruction** Create a new section at the end of this section named "Your work here". In that section, complete the tasks below:

- Make a *subsection* called Wise Words. 
- Put your favorite quote in a block quote. 
- Add a working, clickable link to a website that provides more information about that quote.
- Make another *subsection* called "I recommend", and add some information about your favorite author or musician: 
  - A _subsubheading_ with the name of the artist or author;    
  - An example of their writing or lyrics (formatted in a *block of text*);   
  - A _list_ of things they have written or performed (remember to use the formatting markup for a list!), with any of the titles/names in bold.     

## Your work here

### Wise Words

> "Live as if you were to die tomorrow. Learn as if you were to live forever."

[More information about this quote](https://www.goodreads.com/quotes)

### I recommend

#### Giveon

> "I feel the pain in my chest when I think of you  
> Love comes with heartbreak, that much is true"  

- **Garden Kisses**
- **Tryin Be**
- **Numb**
- **Strangers**
- **Like You**


# Part 2: Code Chunks

```{r, echo= FALSE}
2 + 2
```

Complete the following steps:

- Knit the document and observe what appears in the output.
- Change the chunk option echo=TRUE to echo=FALSE.
- Knit the document again.
- Finally, write 2–3 sentences answering the following questions:
  - What changed between the two outputs?
  - Did the calculation still run when the code was hidden?
  - Why might someone want to hide code in a report?
  
  - Why might someone want to show code in a report?

>Setting echo = FALSE hides the code while still running it and showing the output. This is helpful when the audience only needs to see the results. Showing the code is better when the report is meant for someone who wants to understand or review how the results were produced.
  
# Part 3: A small R-in-markdown preview

- Create a subsection within this section called About this document.
- Write 2–3 sentences describing what this document is and what it produces.
- Include one value generated by inline R code.

## About This Document
>This documents talks about creating subsections and learning how to use formatting tools in Rmarkdown. There are code block that can be implemenet to the file by putting three ticks and putting the letter r in curly braces to code in R. This file also shows that you can hide the code by setting echo = FALSE incase the audience doesnt need to understand R code. Here I will add 4 and 9.

```{r}
4 + 9
```





> To include inline code, use this weird little `r 2+2` pattern, putting the code where I have 2+2 (which is code!) 
> You can use the function `Sys.Date()`, which would be added like this `r Sys.Date()` but you can do something else if you want. (Look at the knit html to see what this does.)

 

# Submitting Instructions

When you are finished: 

- Knit the document so that it produces an html file.
- Stage, commit, and push:
  - The updated `.rmd` file 
  - The generated `.html` file
- Submit the GitHub link to the assignment on Canvas.
 
